\documentclass[12pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}

\title{Automation and Tooling in Modern Software Engineering}
\author{Software Engineering Researcher}
\date{2025}

\begin{document}
\maketitle
\onehalfspacing
https://dl.acm.org/doi/10.1145/361598.361623
\section{Introduction}
Software engineering research increasingly depends on automation to improve productivity and reproducibility. Early discussions on software crises and engineering discipline appear in .
https://link.springer.com/chapter/10.1007/11759744_2
The importance of empirical methods in software engineering is emphasized in https://doi.org/10.1109/TSE.2007.70733.

\section{Version Control Systems}
Distributed version control systems transformed collaboration, as discussed in https://ieeexplore.ieee.org/document/6227223.

An empirical study of GitHub as a collaboration platform can be found in .

Large-scale analysis of open-source development practices is presented in https://arxiv.org/abs/1407.3066.

\section{Continuous Integration}
Continuous Integration improves code quality and feedback cycles according to .

Adoption of CI in GitHub projects is analyzed in https://arxiv.org/abs/1603.00412.

A taxonomy of CI build failures is proposed in https://ieeexplore.ieee.org/document/7962388.

\section{Software Testing}
The role of automated testing in agile development is discussed in .

Mutation testing fundamentals are introduced in 
A comprehensive survey on test case prioritization appears in https://doi.org/10.1109/TSE.2009.42.

\section{Developer Productivity}
Measuring developer productivity remains challenging, as described in https://doi.org/10.1145/2676723.2677271.

An observational study of programmer behavior is presented in https://doi.org/10.1145/3377811.3380383.

The impact of interruptions on software developers is examined in

\section{Documentation and Knowledge Sharing}
The importance of documentation in software projects is discussed in 

Stack Overflow’s role in knowledge sharing is analyzed in 

API documentation practices are evaluated in https://ieeexplore.ieee.org/document/7332459.

\section{Research Software and Reproducibility}
Reproducibility challenges in computational research are discussed in https://doi.org/10.1126/science.1213847.

Best practices for research software engineering are summarized in https://arxiv.org/abs/2006.02330.

A manifesto for reproducible science is presented in https://doi.org/10.1038/533452a.

\section{LaTeX and Scholarly Publishing}
LaTeX’s role in scientific writing is documented in 
Bibliographic data management using BibTeX is described in https://doi.org/10.1145/359460.359482.

Limitations of citation metadata quality are discussed in https://doi.org/10.1145/3448016.3457316.

\section{AI in Software Engineering}
Machine learning for software engineering is surveyed in https://arxiv.org/abs/1709.06182.

AI-assisted code generation is analyzed in https://arxiv.org/abs/2107.03374.

Ethical considerations of AI tools for developers are discussed in https://doi.org/10.1145/3442188.3445922.

\section{Conclusion}
Automation tools continue to reshape how software engineering research is conducted, evaluated, and published, reinforcing the need for reliable tooling as discussed in https://doi.org/10.1145/3368089.3409742.

\end{document}
