\documentclass[12pt]{article}
\usepackage{geometry}

\title{The Omnibus Test: Scientific Milestones}
\author{Stress Tester}
\date{2025}

\begin{document}
\maketitle

\section{Computer Science: AI \& Algorithms}
1. Generative Adversarial Networks (GANs) - ArXiv:
\cite{Goodfellow2014generative}

2. BERT: Pre-training of Deep Bidirectional Transformers - ArXiv:
\cite{Devlin2018bertpretra}

3. Graph Attention Networks - ArXiv:
\cite{Veličković2017graphatten}

4. The original PageRank citation (Google) - Stanford InfoLab:
http://infolab.stanford.edu/~backrub/google.html
% Note: The above might fail if no DOI is found, checking fallbacks.

5. ImageNet Classification (AlexNet) - NIPS (buried DOI):
https://papers.nips.cc/paper/4824-imagenet-classification-with-deep-convolutional-neural-networks

6. A Relational Model of Data (Codd) - ACM:
\cite{Codd1970arelationa}

7. The UNIX Time-Sharing System - ACM:
\cite{Ritchie1974theunixtim}

8. Latent Dirichlet Allocation (LDA) - JMLR:
https://www.jmlr.org/papers/volume3/blei03a/blei03a.pdf
% Note: This is a PDF link. It tests the Unpaywall/PDF extractor.

\section{Physics: From Quantum to Cosmos}
9. Gravitational Waves Observation (LIGO) - APS (Phys Rev Lett):
\cite{Abbott2016observatio}

10. The God Particle (Higgs Boson) - Elsevier (Phys Lett B):
\cite{Aad2012observatio}

11. Theory of Superconductivity (BCS Theory) - APS:
\cite{Bardeen1957theoryofsu}

12. Quantum Entanglement (EPR Paradox) - APS:
\cite{Einstein1935canquantum}

\section{Biology \& Medicine}
14. Structure of DNA (Watson & Crick) - Nature:
\cite{WATSON1953moleculars}

16. Human Genome Sequencing - Nature:
\cite{Hopfner2002therad50zi}
% Note: URL does not have standard "doi.org" prefix but contains the ID.

17. mRNA Vaccines (Kariko/Weissman) - Immunity:
\cite{Karikó2005suppressio}

18. Induced Pluripotent Stem Cells (Yamanaka) - Cell:
\cite{Takahashi2006inductiono}

\section{Chemistry & Materials}
19. Graphene Discovery - Science:
\cite{Novoselov2004electricfi}

20. Click Chemistry (Sharpless) - Angewandte Chemie:
https://onlinelibrary.wiley.com/doi/10.1002/1521-3773(20010601)40:11%3C2004::AID-ANIE2004%3E3.0.CO;2-5

21. Lithium-Ion Batteries (Goodenough) - ACS:
\cite{Chamberlain1983arylisomer}

\section{Mathematics & Economics}
22. The Nash Equilibrium - PNAS:
\cite{Nash1950equilibriu}

23. Prospect Theory (Kahneman/Tversky) - Econometrica:
\cite{Kahneman1979prospectth}

24. The Black-Scholes Model - J. Pol. Econ:
\cite{Black1973thepricing}

25. Perelman's Ricci Flow (Poincare Conjecture) - ArXiv:
https://arxiv.org/abs/math/0211159

\section{Engineering & Tech}
26. The Kalman Filter - ASME:
\cite{Kalman1960anewapproa}

27. Information Theory (Shannon) - Bell Labs:
\cite{Shannon1948amathemati}

28. World Wide Web Proposal (Berners-Lee) - Royal Society:
\cite{Hernández2009amultiform}

29. Public Key Cryptography (RSA) - ACM:
\cite{Rivest1978amethodfor}

\section{Social Sciences & Psychology}
31. The Magical Number Seven (Cognitive capacity) - APA:
\cite{Miller1956themagical}

32. The Strength of Weak Ties (Social Networks) - Sociology:
\cite{Granovetter1973thestrengt}

33. The Tragedy of the Commons (Environmental Sci) - Science:
\cite{Hardin1968thetragedy}

\section{Modern AI (LLMs)}
34. Llama 2: Open Foundation and Chat Models - ArXiv:
\cite{Touvron2023llama2open}

35. LoRA: Low-Rank Adaptation of Large Language Models - ArXiv:
\cite{Hu2021loralowran}

\section{Classic Computing & Math}
36. Computing Machinery and Intelligence (Turing Test) - Mind:
\cite{TURING1950icomputing}

37. New Directions in Cryptography (Diffie-Hellman) - IEEE:
\cite{Diffie1976newdirecti}

\section{Nobel Prize Chemistry}
38. Stratospheric sink for chlorofluoromethanes (Ozone Layer) - Nature:
\cite{Molina1974stratosphe}

\end{document}