\documentclass[12pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}

\title{30 Scientific Milestones for AutoBib Testing}
\author{AutoBib Test Suite}
\date{2025}

\begin{document}
\maketitle
\onehalfspacing

\section{AI and Machine Learning}
\section{Physics and Astronomy}



12. The God Particle (Higgs Boson) - Phys Lett B: \cite{Aad2012observatio}
11. Gravitational Waves Observation (LIGO) - Phys Rev Lett: \cite{Abbott2016observatio}

1. BERT: Pre-training of Deep Bidirectional Transformers - ArXiv: \cite{Devlin2018bertpretra}

2. Graph Attention Networks - ArXiv: \cite{Veličković2017graphatten}

3. GPT-3: Language Models are Few-Shot Learners - ArXiv: \cite{Brown2020languagemo}

4. Transformer Architecture: Attention is All You Need - ArXiv: \cite{Vaswani2017attentioni}

5. Ethical AI: On the Dangers of Stochastic Parrots - ACM: \cite{Bender2021onthedange}

\section{Software Engineering}
6. Continuous Integration, Delivery and Deployment: A Systematic Review - IEEE Access: \cite{Shahin2017continuous}

7. Mutation Testing in the Wild: Findings from GitHub - Springer: \cite{Sánchez2022mutationte}

8. Test-driven development with mutation testing – An experimental study - Springer: \cite{Roman2021testdriven}

9. Empirical Analysis of CI/CD Tools Usage in GitHub Actions Workflows - J. Info. Web Eng.: \cite{Faqih2024empiricala}

10. CI/CD and Automation in DevOps Engineering - AJRCOS: \cite{Chava2024cicdandaut}

\section{Physics and Astronomy}
11. Gravitational Waves Observation (LIGO) - Phys Rev Lett: \cite{Abbott2016observatio}

12. The God Particle (Higgs Boson) - Phys Lett B: \cite{Aad2012observatio}

13. Theory of Superconductivity (BCS) - Phys Rev: \cite{Bardeen1957theoryofsu}

14. Quantum Entanglement (EPR Paradox) - Phys Rev: \cite{Einstein1935canquantum}

15. Hubble's Law: A Relation between Distance and Radial Velocity - PNAS: \cite{Hubble1929arelationb}

\section{Biology and Medicine}
16. Structure of DNA (Watson & Crick) - Nature: \cite{WATSON1953moleculars}

17. Human Genome Sequencing - Nature: \cite{Hopfner2002therad50zi}

18. mRNA Vaccines (Kariko/Weissman) - Immunity: \cite{Karikó2005suppressio}

19. Induced Pluripotent Stem Cells (Yamanaka) - Cell: \cite{Takahashi2006inductiono}

20. CRISPR-Cas9 Genome Editing - Science: \cite{Jinek2012aprogramma}

\section{Chemistry and Materials}
21. Graphene Discovery - Science: \cite{Novoselov2004electricfi}

22. Lithium-Ion Batteries (Goodenough) - J. Am. Chem. Soc.: \cite{Chamberlain1983arylisomer}

23. Haber-Bosch Process - Nature: \cite{ENGELBRETH-HOLM1950production}


24. Human-level control through deep reinforcement learning - Nature:
\cite{Mnih2015humanlevel}
25. OpenCitations: an infrastructure organization for open scholarship  
\cite{Peroni2020opencitati}

\section{Mathematics and Economics}
26. The Nash Equilibrium - PNAS: \cite{Nash1950equilibriu}

27. Prospect Theory (Kahneman/Tversky) - Econometrica: \cite{Kahneman1979prospectth}

28. The Black-Scholes Model - J. Pol. Econ: \cite{Black1973thepricing}

\section{Computer Science and Cryptography}
29. New Directions in Cryptography (Diffie-Hellman) - IEEE: \cite{Diffie1976newdirecti}

30. Computing Machinery and Intelligence (Turing Test) - Mind: \cite{TURING1950icomputing}

\end{document}
