\documentclass[12pt]{article}
\usepackage{geometry}

\title{The Omnibus Test: Scientific Milestones}
\author{Stress Tester}
\date{2025}

\begin{document}
\maketitle

1 BERT: Pre-training of Deep Bidirectional Transformers - ArXiv:
\cite{Devlin2018bertpretra}

2 Graph Attention Networks - ArXiv:
\cite{Veličković2017graphatten}

3 A Relational Model of Data (Codd) - ACM:
\cite{Codd1970arelationa}

4 The UNIX Time-Sharing System - ACM:
\cite{Ritchie1974theunixtim}


\section{Physics: From Quantum to Cosmos}
5 Gravitational Waves Observation (LIGO) - APS (Phys Rev Lett):
\cite{Abbott2016observatio}

6 The God Particle (Higgs Boson) - Elsevier (Phys Lett B):
\cite{Aad2012observatio}

7.Theory of Superconductivity (BCS Theory) - APS:
\cite{Bardeen1957theoryofsu}

8.Quantum Entanglement (EPR Paradox) - APS:
\cite{Einstein1935canquantum}

\section{Biology \& Medicine}
9. Structure of DNA (Watson & Crick) - Nature:
\cite{WATSON1953moleculars}

9. Human Genome Sequencing - Nature:
\cite{Hopfner2002therad50zi}
% Note: URL does not have standard "doi.org" prefix but contains the ID.

10. mRNA Vaccines (Kariko/Weissman) - Immunity:
\cite{Karikó2005suppressio}

11. Induced Pluripotent Stem Cells (Yamanaka) - Cell:
\cite{Takahashi2006inductiono}

\section{Chemistry & Materials}
12. Graphene Discovery - Science:
\cite{Novoselov2004electricfi}

13. Lithium-Ion Batteries (Goodenough) - ACS:
\cite{Chamberlain1983arylisomer}

\section{Mathematics & Economics}
14. The Nash Equilibrium - PNAS:
\cite{Nash1950equilibriu}

15. Prospect Theory (Kahneman/Tversky) - Econometrica:
\cite{Kahneman1979prospectth}

16. The Black-Scholes Model - J. Pol. Econ:
\cite{Black1973thepricing}

\section{Engineering & Tech}
17. The Kalman Filter - ASME:
\cite{Kalman1960anewapproa}

18. Information Theory (Shannon) - Bell Labs:
\cite{Shannon1948amathemati}

19. World Wide Web Proposal (Berners-Lee) - Royal Society:
\cite{Hernández2009amultiform}

20. Public Key Cryptography (RSA) - ACM:
\cite{Rivest1978amethodfor}

\section{Social Sciences & Psychology}
21. The Magical Number Seven (Cognitive capacity) - APA:
\cite{Miller1956themagical}

22. The Strength of Weak Ties (Social Networks) - Sociology:
\cite{Granovetter1973thestrengt}

23. The Tragedy of the Commons (Environmental Sci) - Science:
\cite{Hardin1968thetragedy}

\section{Modern AI (LLMs)}
24. Llama 2: Open Foundation and Chat Models - ArXiv:
\cite{Touvron2023llama2open}

25. LoRA: Low-Rank Adaptation of Large Language Models - ArXiv:
\cite{Hu2021loralowran}

\section{Classic Computing & Math}
26. Computing Machinery and Intelligence (Turing Test) - Mind:
\cite{TURING1950icomputing}

27. New Directions in Cryptography (Diffie-Hellman) - IEEE:
\cite{Diffie1976newdirecti}

\section{Nobel Prize Chemistry}
28. Stratospheric sink for chlorofluoromethanes (Ozone Layer) - Nature:
\cite{Molina1974stratosphe}

\section{Astronomy & Vision}
29. A Relation between Distance and Radial Velocity (Hubble's Law) - PNAS:
\cite{Hubble1929arelationb}

30. Learning Transferable Visual Models (CLIP / OpenAI) - ArXiv:
\cite{Radford2021learningtr}
\end{document}